Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-20 src/tex/ms.tex
Update tesxt

Due to the number of calibration parameters (often in a couple hundreds if not
more), waveform models is usually calibrated in pieces \citep{fill}. This
ignores the correlation between different parts of the waveform model and limits
it quality. Recently, there has been efforts in rebuilding waveform models
\citep{fill} that supports automatic differentiation (AD)\citep{fill}, which is
a technique used to compute derivatives of functions down to machine precision
without issues of scaling up to high dimension or expression swelling. In
particular, {\ripple} \citep{ripple} exposes the calibration parameters to the
user. This allows us to make use of infrastructures that are heavily used in
machine learning, such as gradient descent and back propagation\cite{fill}, to
improve the calibration of the waveform models.

% Put more focus on the joint optimization instead of having a set of more accurate 
% coefficients, since the method is the main point
In this paper, we investigate the possibility of further improving the accuracy
of a waveform model, IMRPhenomD\citep{fill}, by jointly optimizing all the
calibration coefficients given a set of NR waveforms. Training on a small number
of NR waveforms, we demonstrate one can improves the match between IMRPhenomD
and NR waveforms over a decently sized parameter space, up to mass ratio $q=8$
We also explore how different parts of the source parameter space (e.g. the
primary and second spins) respond to the optimization procedure, by optimizing
the waveform separately for different regions of the parameter space. This gives
us hints on whether the waveform model performs equally well in different
regions of the parameter space.

>>>>

Because of the large number of calibration parameters (often in a couple hundreds if not
more), waveform models is usually calibrated in pieces \citep{fill}. This
ignores the correlation between different parts of the waveform model and limits
it quality. Recently, there has been efforts in rebuilding waveform models
\citep{fill} that supports automatic differentiation (AD)\citep{fill}, which is
a technique used to compute derivatives of functions down to machine precision
without issues of scaling up to high dimension or expression swelling. In
particular, {\ripple} \citep{ripple} exposes the calibration parameters to the
user. This allows us to make use of infrastructures that are heavily used in
machine learning, such as gradient descent and back propagation\cite{fill}, to
improve the calibration of the waveform models.

% Put more focus on the joint optimization instead of having a set of more accurate 
% coefficients, since the method is the main point
In this paper, we investigate the possibility of further improving the accuracy
of a waveform model, IMRPhenomD\citep{fill}, by jointly optimizing all the
calibration coefficients given a set of NR waveforms. Training on a few NR
waveforms, we demonstrate one can improve the match between IMRPhenomD and NR
waveforms over a decently sized parameter space, up to mass ratio $q=8$ We also
explore how different parts of the source parameter space (e.g. the primary and
second spins) respond to the optimization procedure, by optimizing the waveform
separately for different regions of the parameter space. This gives us hints on
whether the waveform model performs equally well in different regions of the
parameter space.
